---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Submission

<!-- badges: start -->
[![Build Status](https://travis-ci.org/larkinj/Submission.svg?branch=master)](https://travis-ci.org/larkinj/Submission)
<!-- badges: end -->

This package is published as part of the Building an R Package coursera course.

## Installation

You can install the released version of Submission from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Submission")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("larkinj/Submission")
```
## Example

## Package Details
The Fatality Analysis Reporting System (FARS) is a nationwide census prepared by the US National Highway Traffic Safety Administration.
It provides the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

This package helps to use FARS data in your analysis. Filenames can be created programmatically using the make_filename function:
```{r}
library(Submission)
farsFile <- file.path("..","data",make_filename(2013))
```

To load a FAR file use the far_read function:
```{r}
head(fars_read(farsFile))
```
